High-Throughput Computing on \\ High-Performance Platforms: A Case Study

### 2017-09-10 nge.tex
more comments fixe.

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 3: The first paragraphs of section V. are basically a
	rediscovery of the advantages of pilot jobs for WLCG task scheduling.
	Since all those pain points were well-known in the WLCG community before
	the project started, it should be explained why a pilot job approach was
	not taken in the first place.\mtnote{Added an opening paragraph recalling
	the explanation offered in \S\ref{sec:panda_titan}}.
	\item REVIEWER 3: Figure 6. refers to a "User Workstation" as the running
	place for the Pilot and Unit Managers, which is never mentioned in the
	text. (I got the impression that the NGE would run on a DTN node; if this
	is not the case and separate workstations are being used for the testing
	phase, this should be made clear.)\mtnote{Fixed.}
\end{itemize}
\fi

>>>>

\ifreview
Comments to address in this section:
\begin{itemize}
	\color{red} 
	\item REVIEWER 3: The first paragraphs of section V. are basically a
	rediscovery of the advantages of pilot jobs for WLCG task scheduling.
	Since all those pain points were well-known in the WLCG community before
	the project started, it should be explained why a pilot job approach was
	not taken in the first place.\mtnote{Added an opening paragraph recalling
	the explanation offered in \S\ref{sec:panda_titan}}.
	% \item REVIEWER 3: Figure 6. refers to a "User Workstation" as the running
	% place for the Pilot and Unit Managers, which is never mentioned in the
	% text. (I got the impression that the NGE would run on a DTN node; if this
	% is not the case and separate workstations are being used for the testing
	% phase, this should be made clear.)\mtnote{Fixed.}
\end{itemize}
\fi
